Immutable Source-Mapped Abstract Syntax Tree:\ \, \\ A Design Pattern for Refactoring Engine APIs

### 2017-09-27 paper.tex
made solution bold

Traditionally, fine-grained program syntax is made available through 
abstract syntax trees.

@@

Refactorings, however, are complicated by the C preprocessor. The grammar of 
preprocessor directives doesn't take into account C syntax, and can't be easily
represented in the C AST. This is the subject of Garrido's entire Ph.D.~thesis~%
\cite{garrido05program}. The compiler's method of preprocessing before parsing
can't be used, because the unpreprocessed text is what must be edited. The 
refactoring too must be able to parse, analyze, and transform code \textit{
with embedded preprocessor directives.}

@@

\textit{Use a parser for the language being refactored to construct an
\textup{abstract syntax tree}, or \textup{AST}.  Make the AST
\textup{immutable}---i.e., its structure cannot be changed---but provide
\textup{source mapping} information so that every node in the AST can be mapped
to a particular substring of the original source code. Treat the source code
as a string, and use the source code location information from the AST to
add, replace, and delete substrings.}

>>>>

Typically, fine-grained program syntax is made available through 
abstract syntax trees.

@@

Refactorings, however, are complicated by the C preprocessor. The grammar of 
preprocessor directives doesn't take into account C syntax, and can't be easily
represented in the C AST. This is the subject of Garrido's entire Ph.D.~thesis~%
\cite{garrido05program}. The compiler's method of preprocessing before parsing
can't be used, because the unpreprocessed text is what must be edited. The 
refactoring too must be able to parse, analyze, and transform code \textit{with embedded preprocessor directives.}

@@

\textbf{Use a parser for the language being refactored to construct an
\textit{abstract syntax tree}, or \textup{AST}.  Make the AST
\textit{immutable}---i.e., its structure cannot be changed---but provide
\textit{source mapping} information so that every node in the AST can be mapped
to a particular substring of the original source code. Treat the source code
as a string, and use the source code location information from the AST to
add, replace, and delete substrings.}
